How Safe is Campas Really? Assault Rate Trends Within and Around the University of Toronto: A Ten-Year Analysis

### 2024-01-24 outputs/paper/paper.qmd
Added my maps.

```{r}
THIS IS FOR MY PHOTO
```

###University of Toronto Neighbourhoods
The 'Neighbourhood Crime Rates' dataset was filtered to focus solely on assault rates. This entailed discarding unrelated crime statistics and zeroing in on annual assault rate data per neighbourhood. The next crucial step was to narrow down the neighbourhoods to the four aforementioned areas central to the University of Toronto. These neighbourhoods are 4 of the 158 legitamate neighbourhoods recognized by the city of Toronto and can be seen in figure (PICTURE REF> HERE). This selective focus was vital to the study's goal of examining crime trends in university-adjacent areas (See Table \@ref(tbl-cleaned_uoft_neighbourhood_data)).

@@

###University of Toronto Surrounding Areas
The scope was then expanded to encompass neighbourhoods surrounding the primary four that make up the University of Toronto. This was done to understand the peripheral impact and the broader context of assault rates around the university. This secondary cleaning phase involved identifying and including adjacent neighbourhoods, thereby painting a more holistic picture of the university's neighbourhood safety landscape (See Table \@ref(tbl-cleaned_surrounding_neighbourhood_data)). These neighbourhoods make up 10 of the 158 legitimate neighbourhoods recognized by the city of Toronto and can be seen in figure (PICTURE REF> HERE).

>>>>

###University of Toronto Neighbourhoods
The 'Neighbourhood Crime Rates' dataset was filtered to focus solely on assault rates. This entailed discarding unrelated crime statistics and zeroing in on annual assault rate data per neighbourhood. The next crucial step was to narrow down the neighbourhoods to the four aforementioned areas central to the University of Toronto. These neighbourhoods are 4 of the 158 legitimate neighbourhoods recognized by the city of Toronto and can be seen in (@ref(fig-uoft_neighbourhood_map)). This selective focus was vital to the study's goal of examining assault trends in university-adjacent areas (See Table \@ref(tbl-cleaned_uoft_neighbourhood_data)).

```{r}
#| message: false
#| echo: false
#| label: fig-uoft_neighbourhood_map
#| fig-cap: Map of UofT Neighbourhoods

knitr::include_graphics("/cloud/project/inputs/sketches/uoft_neighbourhoods.png")
```

@@

###University of Toronto Surrounding Areas
The scope was then expanded to encompass neighbourhoods surrounding the primary four that make up the University of Toronto. This was done to understand the peripheral impact and the broader context of assault rates around the university. This secondary cleaning phase involved identifying and including surrounding neighbourhoods, thereby painting a more holistic picture of the university's neighbourhood safety landscape (See Table \@ref(tbl-cleaned_surrounding_neighbourhood_data)). These neighbourhoods make up 9 of the 158 legitimate neighbourhoods recognized by the city of Toronto and can be seen in (@ref(fig-surrounding_neighbourhood_map)).

```{r}
#| message: false
#| echo: false
#| label: fig-surrounding_neighbourhood_map
#| fig-cap: Map of All 13 Neighbourhoods

knitr::include_graphics("/cloud/project/inputs/sketches/surrounding_neighbourhoods.png")
```
